%! TEX root = /Users/manunavjeevan/Documents/UCLA/Third Year/Reading Group/wcep.tex

We now want to show a Donsker Theorem using bracketing numbers. The proof is more involved than for the Glivenko-Cantelli Theorem (Theorem~\ref{thm:vdv2.4.1}) using bracketing numbers, so we may not get too far into it here. 

To show this theorem we make minor use of the following Lemma from VdV\&W, given below
\begin{lemma}[Problem 2.5.5 VdV\&W]
	\label{lemma:vdv2.5.5}
	For each positive random variable \(X\) one has the following inequality
	\begin{equation*}
		\sup_{t>0}t\E X\mathds{1}\{X > t\} \leq  2 \|X\|_2^2 
	\end{equation*}
\end{lemma}

\begin{theorem}[Donsker Theorem for Bracketing Numbers]
	\label{thm:donsker-bracketing}
	Let \(\calF\) be a class of measurable functions with an envelope \(F\) such that \(P^\star F^2 < \infty\) and
	\begin{equation}
		\label{eq:donsker-bracketing-condition}
		\int_{0}^{\infty} \sqrt{\log\calN_{[\hspace{0.1em}]}\left(\eps,\calF,L_2(P)\right)}\;d\eps <\infty
	\end{equation}
	then \(\calF\) is Donsker.
\end{theorem}
\begin{proof}
	The proof of this is roughly based on the steps in Theorem 2.5.6 in VanDerVaart and Wellner. I attempt to replicate the argument below:

	For each \(q\in\SN\) there is a partition \(\calF = \bigcup_{i=1}^{N_q} \calF_{qi}\) of \(\calF\) into \(N_q\) disjoint subsets such that 
	\begin{align*}
		\sum_{i=1}^{\infty} 2^{-q} \sqrt{\log N_q} &< \infty \\	
		\|\big(\sup_{f,g\in\calF_{qi}}|f-g|\big)^\star\|_{P,2} &< 2^{-q} \\
		\sup_{f,g\in\calF_{qi}} \|f-g\|_{P,2} &< 2^{-q}
	\end{align*}
	To see this, cover \(\calF\) with a minimal numbers of \(L_2(P)\) balls and \(L_2(P)\) brackets of size \(2^{-q}\), disjointify and take the intersection of the two partitions. By definition of the \(2^{-q}\) balls and \(2^{-q}\) brackets, the last two conditions hold. To see that the first condition holds note that the integral of the bracketing number being finite implies that the integral of the covering number is finite, and that \(\calN_{[\hspace{0.1em}]}\) and \(\calN\) are decreasing in \(\eps\). For any decreasing function \(f\) it is clear that
	\[
		\sum_{i=1}^n 2^{-q} f(q) \leq \int_0^\infty f(q)\;dq
	.\]
	which gives us the first condition. This sequence of partitions can, without loss of generality, be chosen as successive refinements.
	\footnote{To see this, construct a sequence of partitions \(\calF = \bigcup_{i=1}^{\bar N_q} \bar\calF_{qi}\) without this property. Next, take the partition at stage \(q\), \(\calF = \bigcup_{i=1}^{N_q}\calF_{qi}\) to consists of all intersections of the form \(\bigcap_{p=1}^q \bar\calF_{p,i_p}\) (basically take the intersection of all partitions up till \(q\)) so that \(|N_q| = \prod_{p=1}^q \bar N_p\). Using the inequality \(\big(\log\prod\bar N_p\big)^{1/2} \leq \sum \big(\log \bar N_p\big)^{1/2}\)  we get that:
	\begin{align*}
		\sum_{q=1}^\infty 2^{-q} \sqrt{\log N_q} &\leq \sum_{q=1}^\infty 2^{-q} \sum_{p=1}^q \log \sqrt{\bar N_p} \\
												 &= \sum_{q=1}^\infty 2^{-q} \sum_{p=1}^\infty 2^{-p}\sqrt{\log \bar N_p}\\
												 &< \infty
	\end{align*}
	The equality is a bit difficult to see but follows from the preceding line after rewriting the double summation as a triangular array. To simplify, consider an infinite sequence \(\{a_i\}_{i=1}^n\). Then \(\sum_{i=1}^\infty 2^{-i} \sum_{j=1}^i a_i  = a_1 + \frac{1}{2}(a_1 + a_2) + \frac{1}{2^{2}}(a_1 + a_2 + a_3) + \dots\). Rearrange to get the result. This gives us that the first condition still holds for the new nesting sequence of partitions. The second and third conditions trivially still hold as the new partitions are finer than the previous ones.  
	}

	For each \(q\) choose a fixed element \(f_{qi}\) from each partitioning set \(\calF_{qi}\) and define \(\pi_qf = f_{qi}\) if \(f \in \calF_{qi}\). Further define \(\Delta_q f = \sup_{f,g\in\calF_{q,i}} |f-g|^\star\) if \(f\in\calF_{qi}\).

	Note that \(\pi_q f\) and \(\Delta_q f\) take on one of \(N_q\) values as \(f\) ranges through \(\calF\). In view of Theorem~\ref{thm:vdv1.5.6} it suffices to show that the sequence \(\|\mathbb{G}_n(f-\pi_{q_0}f)\|_\calF\) converges in probability to zero as \(n\to\infty\) for an arbitrary \(q_0\) and then take \(q_0 \to \infty\).

	Define for each fixed \(n\) and sufficiently large \(q \geq q_0\) the following numbers and indicator functions:
	\begin{align*}
		a_q &= 2^{-q}/\sqrt{\log N_{q+1}} \\
		A_{q-1}f &= \mathds{1}\{\Delta_{q0}f \leq \sqrt n a_{q_0} \wedge \dots\wedge \Delta_{q-1}f \leq \sqrt{n} a_{q-1}\}\\
		B_q f &= \mathds{1}\{\Delta_{q_0}f \leq \sqrt{n}a_{q_0}\wedge\dots\wedge \Delta_{q-1}f \leq \sqrt{n}a_{q-1}\wedge \Delta_q f > \sqrt{n} a_q \}\\
		B_{q_0} &= \mathds{1}\{\delta_{q_0}f > \sqrt{n}a_{q_0}\} 
	\end{align*}
	Note that \(A_qf\) and \(B_qf\) are constant in \(f\) on each of the partitioning sets \(\calF_{qi}\) at level \(q\) because the partitions are nested.\footnote{Recall that \(\Delta_q f\) is the same for all elements in \(\calF_{q,i}\) and that \(\calF_{qi} \subset \calF_{(q-1)i}\)}

	Now, pointwise in \(x\), decompose
	\begin{align}
		\label{eq:decomposition}
		\tag{B-1}
		f - \pi_{q_0}f = (f-\pi_{q_0}f)B_{q_0}f + \sum_{q= q_0+1}^\infty (f-\pi_qf)B_qf + \sum_{q=q+1}^\infty (\pi_qf-\pi_{q-1}f)A_{q-1}f  
	\end{align}
	Here note that we are essentially decomposing the event space into \(B_{q_0}\) and \(B_{q_0}^c = A_{q_0}\). We can think of \(B_q\) as \(f\) being ``between'' \(A_{q-1}\) and \(A_{q}\). That is, if all the conditions for \(B_q\) hold except for the last one, then \(A_{q-1}\) is equal to \(1\) and \(B_q\) is equal to zero. Conversely if \(B_q\) is equal to one, then all the conditions for \(A_q\) hold except for the last one (\(\Delta_q g \leq \sqrt{n} a_{q}\)) so \(A_q\) is equal to zero and \(B_q\) is equal to one. Equivalently \(A_{q-1} + B_q = A_q\) or \(A_q - A_{q-1} = B_q\). Combine this with the fact that sets indicated \(A_q\) are nested and telescope to get the decomposition above.  

	Now we will apply the empirical process \(\mathbb{G}_n = \sqrt{n}\left(\P_n-P\right)\) to each of the terms in~\eqref{eq:decomposition} and take the suprema over \(f\in\calF\). We will show that each of the resulting 3 variables converge to zero in probability and then take \(q_0 \to \infty\).

	First, since \(|f-\pi_{q_0}f|B_{q_0}f \leq 2F\mathds{1}\{2F > \sqrt{n}a_{q_0}\}\) one has that\footnote{Recall the definition of the ``\(\calF\)'' norm, pull out the \(\sqrt{n}\), apply triangle inequality and note that \(\E^\star\P_n F \leq \E^\star F\) because \((S+ T)^\star \leq S^\star + T^\star\) for any functions \(S,T\). } 
	\[
		\E^\star\|\mathbb{G}_n(f-\pi_{q_0}f)B_{q_0}f\|_\calF \leq 4\sqrt{n}P^\star F\mathds{1}\{2F > \sqrt{n}a_{q_0}\} 
	.\] 
	The right hand size converges to zero as \(n\to\infty\) because \(F\) has a finite second outer moment.

	Second, since the partitions are nested, \(\Delta_q f B_q f \leq  \Delta_{q-1}fB_qf\) and applying Lemma~\ref{lemma:vdv2.5.5}:



\end{proof}

